PANCHANGE_data_preprocessing

### 2020-08-14 PANCHANGE_data_preprocessing2020-07-15.Rmd
adapted ocir prepan

```{r edgi ocir prepan cleaning}
if(EDGI == TRUE){
  edgi.ocir.raw.id <- edgi.ocir.raw %>%
    drop_na(externalDataReference) %>% # Drop NAs
    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
    mutate(ID = as.numeric(ID)) %>%
    select(
      Sample, # Sample
      ID, # ID
      ocir.i_repeatedly_check_doors_windows_drawers_etc_prepan = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
      ocir.arranged_things_change_upset_prepan = ocir.arranged_things_change_upset,
      ocir.repeat_feel_numbers_prepan = ocir.repeat_feel_numbers,
      ocir.clean_simply_wash_feel_prepan = ocir.clean_simply_wash_feel,
      ocir.mind_upset_unpleasant_thoughts_prepan = ocir.mind_upset_unpleasant_thoughts,
      ocir.afraid_avoid_throwing_things_prepan = ocir.afraid_avoid_throwing_things,
      ocir.light_switches_water_taps_prepan = ocir.light_switches_water_taps,
      ocir.arranged_things_prepan = ocir.arranged_things,
      ocir.good_feel_bad_numbers_prepan = ocir.good_feel_bad_numbers,
      ocir.hands_longer_wash_prepan = ocir.hands_longer_wash,
      ocir.saved_things_prepan = ocir.saved_things,
      ocir.frequently_difficulty_rid_nasty_prepan = ocir.frequently_difficulty_rid_nasty,
      ocir.i_check_things_more_often_than_necessary_prepan = ocir.i_check_things_more_often_than_necessary.,
      ocir.arranged_properly_objects_upset_prepan = ocir.arranged_properly_objects_upset,
      ocir.feel_compelled_count_things_prepan = ocir.feel_compelled_count_things,
      ocir.strangers_touch_touched_difficult_prepan = ocir.strangers_touch_touched_difficult,
      ocir.control_difficult_find_thoughts_prepan = ocir.control_difficult_find_thoughts,
      ocir.i_collect_things_i_dont_need_prepan = ocir.i_collect_things_i_dont_need
    ) %>%
    add_numeric(., exclude = exclude_cols) %>%
    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
    mutate_if(is.numeric, ~na_if(., -99)) %>%
    mutate_if(is.numeric, ~na_if(., -77)) %>%
    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))

>>>>

```{r edgi ocir prepan cleaning}
if(EDGI == TRUE){
  edgi.ocir.raw.id <- edgi.ocir.raw %>%
    drop_na(externalDataReference) %>% # Drop NAs
    distinct(externalDataReference, .keep_all = TRUE) %>% # Remove duplicates based on ID
    separate(externalDataReference, into = c("Sample", "ID"), sep = 4) %>% # Split ID in Sample and Number
    mutate(ID = as.numeric(ID)) %>%
    select(
      Sample, # Sample
      ID, # ID
      ocir.i_repeatedly_check_doors_windows_drawers_etc_prepan = ocir.i_repeatedly_check_doors_windows_drawers_etc.,
      ocir.arranged_things_change_upset_prepan = ocir.arranged_properly_objects_upset, # different GLAD: ocir.arranged_things_change_upset,
      ocir.repeat_feel_numbers_prepan = ocir.repeat_feel_numbers.87, # ocir.repeat_feel_numbers,
      ocir.clean_simply_wash_feel_prepan = ocir.clean_simply_wash_feel.9, # ocir.clean_simply_wash_feel,
      ocir.mind_upset_unpleasant_thoughts_prepan = ocir.mind_upset_unpleasant_thoughts.11, # ocir.mind_upset_unpleasant_thoughts,
      ocir.afraid_avoid_throwing_things_prepan = ocir.afraid_avoid_throwing_things.7, # ocir.afraid_avoid_throwing_things,
      ocir.light_switches_water_taps_prepan = ocir.light_switches_water_taps.7, # ocir.light_switches_water_taps,
      ocir.arranged_things_prepan = ocir.arranged_things.32, # ocir.arranged_things,
      ocir.good_feel_bad_numbers_prepan = ocir.good_feel_bad_numbers.60, # ocir.good_feel_bad_numbers,
      ocir.hands_longer_wash_prepan = ocir.hands_longer_wash.23, # ocir.hands_longer_wash,
      ocir.saved_things_prepan = ocir.saved_things,
      ocir.frequently_difficulty_rid_nasty_prepan = ocir.frequently_difficulty_rid_nasty.16, # ocir.frequently_difficulty_rid_nasty,
      ocir.i_check_things_more_often_than_necessary_prepan = ocir.i_check_things_more_often_than_necessary.,
      ocir.arranged_properly_objects_upset_prepan = ocir.arranged_properly_objects_upset,
      ocir.feel_compelled_count_things_prepan = ocir.feel_compelled_count_things.27, # ocir.feel_compelled_count_things,
      ocir.strangers_touch_touched_difficult_prepan = ocir.strangers_touch_touched_difficult.33, # ocir.strangers_touch_touched_difficult,
      ocir.control_difficult_find_thoughts_prepan = ocir.control_difficult_find_thoughts.30, #ocir.control_difficult_find_thoughts,
      ocir.i_collect_things_i_dont_need_prepan = ocir.i_collect_things_i_dont_need.348, # ocir.i_collect_things_i_dont_need
    ) %>%
    add_numeric(., exclude = exclude_cols) %>%
    mutate_if(is.numeric, ~na_if(., -88)) %>% # Recode missing values to NAs in numeric variables
    mutate_if(is.numeric, ~na_if(., -99)) %>%
    mutate_if(is.numeric, ~na_if(., -77)) %>%
    mutate_if(is.factor, ~na_if(., "Seen but not answered")) %>% # Recode missing values to NAs in factor variables
    mutate_if(is.factor, ~na_if(., "Don't know")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to say")) %>%
    mutate_if(is.factor, ~na_if(., "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Seen but not answered")) %>% # Drop empty factor levels
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Don't know")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to answer")) %>%
    mutate_if(is.factor, ~forcats::fct_drop(., only = "Prefer not to say"))
